Application-Level Regression Testing Framework using Jenkins

### 2017-03-23 manuscript/manuscript.tex
Worked on SSH method. Tim's previous write up has been incorporated here (and is now commented out).

\subsection{Master-Node Configuration}
We added a standard user account to our cluster that will execute the Jenkins tests. Unique ssh keys were generated on the Jenkins Server for accessing the user account on production and test environments.  The keys on the server are located in Jenkins home directory (/var/lib/jenkins/.ssh). Using the GUI management console, the keyfile location and passphrase was entered under Manage Jenkins, Configure System, SSH remote hosts section. A unique SSH site is configured for our TDS, production and development login nodes.

\subsection{Accessing Login Nodes}
The ssh public key generated on Jenkins Server was deployed in the login node user account. The login node sshd_config was modified to allow Public Key Authentication from the Jenkins Server IP.

>>>>

\subsection{Using SSH Plugins for Test Systems}
The SSH plugin (FIXME: Need references) is another method for which one can access the HPC systems from Jenkins. As the name implies, Jenkins project with this type of build scripts simply SSH to the desired machine then execute the scripts there.

The benefit of this method is that it more closely mimmicks (FIXME; spelling) how real users access the HPC system. There is no need for additional daemon to run on the HPC login nodes and there is no need for the corresponding opening of port on Jenkins VM. Because NCSA and NICS systems utilize two-factor RSA one-time password for users login, we needed to make slight modification so that Jenkins can have automated login. The login nodes \textttt{/etc/ssh/sshd_config} was modified to allow ''Public Key Authentication`` from the Jenkins VM unique IP address. Pairs of SSH keys with passphrase were generated on Jenkins VM with their public keys deployed on the appropriate login nodes to allow for passwordless login. The SSH plugins allow one to manage which key (and passphrase) to use with which system. The keys on Jenkins VM are located under Jenkins home directory (by default \texttt{/var/lib/jenkins/.ssh}. Although configuring all of these could be somewhat tedious, once everything is set Jenkins should be able to run scripts on the intended HPC systems via SSH. For testing our setup, we created simple Jenkins projects whose task is to print out the \texttt{\$HOSTNAME} of the system.

The drawback of this method is that one has to manage almost all data management explicitly. If one checks out or clones a repository on Jenkins (part of Jenkins core feature), it need to be explicitly copied (e.g. with \texttt{rsync} or \texttt{scp}) to the remote system. Any files generated by the tests that need to be read by Jenkins (e.g. plot file) needs to be copied back explicitly to the Jenkins VM. A related drawback is that one must explicitly ensure that the build environment is ''clean`` on the remote system (e.g. no left over files or data from previous run). This is because although Jenkins can clean up its workspace, this workspace (in Jenkins perspective) exists only on the VM. The remote systems' workspaces are out of reach from Jenkins. This drawback also prevents one to easily allow concurrent builds of the same project.

%\subsection{Master-Node Configuration}
%We added a standard user account to our cluster that will execute the Jenkins tests. Unique ssh keys were generated on the Jenkins Server for accessing the user account on production and test environments.  The keys on the server are located in Jenkins home directory (/var/lib/jenkins/.ssh). Using the GUI management console, the keyfile location and passphrase was entered under Manage Jenkins, Configure System, SSH remote hosts section. A unique SSH site is configured for our TDS, production and development login nodes.

%\subsection{Accessing Login Nodes}
%The ssh public key generated on Jenkins Server was deployed in the login node user account. The login node sshd_config was modified to allow Public Key Authentication from the Jenkins Server IP.
